% $Id$
%==============================================================================
\section{CCM Tools Component Model}
\label{section:CcmtoolsComponentModel}
%==============================================================================

A component type is a specific, named collection of features that can be
described by an {\bf Interface Definition Language} (IDL) and encapsulates its
internal representation and implementation.


%------------------------------------------------------------------------------
\subsection{Component Ports}
%------------------------------------------------------------------------------

Components support a variety of surface features through which clients and other
components may interact with a component. These surface features are called
ports.

The CCM Tools component model supports three kinds of ports:
\begin{description}
\item [Attributes] which are named values exposed through getter and setter
methods. Attributes are primarily intended to be used for component configuration.

\item [Facets] which are distinct named interfaces provided by the component
for client interaction.


\item [Receptacles] which are named connection points that describe the
component's ability to use a reference supplied by some external agent.
\end{description}

The component has a single distinguished reference whose interface conforms to
the component definition.
This reference supports an interface, called the component's 
{\bf equivalent interface} which allows clients to navigate among the
component's facets, and to connect to the component's ports.



%------------------------------------------------------------------------------
\subsection{Component Home}
%------------------------------------------------------------------------------

A component home acts as a manager for instances of a specified component type.



%------------------------------------------------------------------------------
\subsection{Component Life Cycle}
%------------------------------------------------------------------------------

\newpage
