%==============================================================================
\chapter{Confix Installation}
%==============================================================================
\begin{flushright}
{\it }
\end{flushright}

%------------------------------------------------------------------------------
\section{Prerequisites}
%------------------------------------------------------------------------------
To install Confix, the following programs must be available:

\begin{itemize}
\item Python, at least version 2.1.3.
\item Automake, at least version 1.5.
\item Autoconf, at least version 2.52.
\item Libtool. Support for Libtool is optional in Confix, so you may leave
it out entirely. Version 1.4.3 has been reported to give occasional
errors, 1.4.2 and 1.5 are ok.
\end{itemize}


%------------------------------------------------------------------------------
\section{How to get it}
%------------------------------------------------------------------------------

The project's homepage it hosted on Sourceforge,
{\tt http://confix.sourceforge.net}. See there for releases,
announcements et cetera.

%------------------------------------------------------------------------------
\section{Source distribution}
%------------------------------------------------------------------------------
Unpack the file, point the {\tt PYTHONPATH} environment variable into
the root directory of the Confix package, and your {\tt PATH}
environment variable into the {\tt scripts} subdirectory thereof. For
example,
\begin{verbatim}
$ tar zxplf Confix-x.y.z.tar.gz
\end{verbatim}

Then make a call to Distutils to build and install the source.
\begin{verbatim}
$ cd Confix-1.0.1.tar.gz
$ pwd
/home/jfasch/Confix-1.0.1
$ python setup.py install --prefix=<confix_path>
\end{verbatim}

Then, provided the prefix you gave wasn't a standard one like
{\tt /usr} or {\tt /usr/local}, you should update your environment
accordingly. For example, you could add the following lines to your
{\tt ~/.bashrc},
\begin{verbatim}
PREFIX=<confix_path>
export PYTHONPATH=$PYTHONPATH:$PREFIX/lib/pythonA.B/site-packages
export PATH=$PATH:$PREFIX/bin
\end{verbatim}

Make sure A.B corresponds to the version of Python that you use, such
as 2.1 or 2.2.
