% $Id$
%==============================================================================
\section{Light Weight CORBA Component Model}
%==============================================================================

Many of today's embedded CORBA applications are unable to use the available 
enterprise CCM due to design constraints.
These constraints include small code size in embedded environments and 
limited processing overhead for performance conservative applications.

\vspace{3mm}
\noindent
To overcome this problem, LwCCM
was submitted to the OMG \cite{LwCCM-Specification}.
The purpose of this profile is to specify a lightweight version of the CCM.
The principal aim of LwCCM is to have a component model sufficient to compose
applications with CORBA components without all optional features that are
not part of the ``core'' capabilities of CCM.
%This profile exposes what mandatory features should be contained in a 
%minimum implementation of the CCM. 
The choices made in the profile follow rules established to suit embedded
environments:
\begin{itemize}
\item {\bf Redundancy.}
If several ways of requesting a service exist, only one is retained.

\item {\bf Interoperability and Compatibility with full CCM.}
During deployment, a leightweight component should be deployable by a full
CCM deployment application. Connections between a leightweight component
and a full CCM component must be possible.
Implementations of leightweight components should be source compatible
with the full CCM.

\item {\bf Persistence.}
The LwCCM does not need to manage any kind of persistence as described in the
CCM specification. 

\item {\bf Transactions.}
Transactions are not a feature commonly used in embedded systems thus they
are not included in the LwCCM profile.

\item {\bf Security.}
Security will not be treated in the LwCCM profile.

\item {\bf Introspection.}
Not all introspection operations are retained in this profile because they
are not essential to perform the deployment of components.

\item {\bf EJB Integration.}
There is no integration of {\it Enterprise JavaBeans} defined in LwCCM
because EJB are not required for embedded targeted environments.

\item {\bf Deployment and Configuration.}
Instead of the {\it Packaging and Deployment} chapter of CCM, LwCCM
is based on the OMG {\it Deployment and Configuration} specification 
\cite{DeploymentAndConfiguration}.
This includes also the definitions of component and assembly descriptor
files and their XML DTDs.

\item {\bf CCM Implementation Framework.}
The whole {\it Component Implementation Definition Language} (CIDL) chapter 
as well as the {\it CCM Implementation Framework} (CIF) chapter are excluded 
from the LwCCM profile.

The CIDL is redundent with IDL definitions because all functional descriptions
of the component (facets, reseptacles, events and attributes) is done with the 
IDL files.
The way to assign a component category (service or session) to a component
can be done via an XML description file that will be used with the IDL files to
generate container code and skeletons.
\end{itemize}

\noindent
This profile tries to be as compliant as possible to the OMG 
{\bf Minimum CORBA} and {\bf Lightweight Services} specifications 
\cite{Minimum_CORBA, LightweightServices}.


